### 2019-08-14 Writeup/Thesis/pages/introduction.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

A countermeasure for this is the verification of each parties' key fingerprint. A fingerprint is a small string of characters that is unique to each key pair. Therefore, it can be used as as a way of identification.

Fingerprints can come in a number of different encodings such as hexadecimal, words and even procedurally generated avatars. Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing the scheme to be user friendly is a task of upmost importance.

Humans have long been known as the most vulnerable part of any system. To combat this issue, solutions have been proposed to remove the manual verification with examples such as PGP's web-of-trust\cite{callas1998openpgp} and Namecoin\cite{kalodner2015empirical}. However, these suffer from user adoption due to perceived complexity. This leaves manual verification in the current position of being a difficult problem, where the proposed solutions need to sacrifice one of usability or security. Therefore, research into improving or creating new fingerprint encodings that work well with users remains massively relevant.

The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as it claims at this point have been unsubstantiated.

@@

\textbf{Chapter 4} documents the prosed designs required to answer the research questions proposed in Chapter 3.

@@

\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside the any conclusions that can be drawn from the research.

>>>>

A countermeasure for this is the verification of each parties' key fingerprint. A fingerprint is a small string of characters that is unique to each key pair. Therefore, it can be used as a way of identification.

Fingerprints can come in a number of different encodings such as hexadecimal, words and even procedurally generated avatars. Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing of user friendly schemes a task of upmost importance.

Humans have long been known as the most vulnerable part of any system. To combat this issue, solutions have been proposed to remove the manual verification with examples such as PGP's web-of-trust\cite{callas1998openpgp} and Namecoin\cite{kalodner2015empirical}. However, these suffer from user adoption due to perceived complexity. This leaves manual verification in a difficult position, due the proposed solutions needing to sacrifice either usability or security. Therefore, research into improving or creating secure fingerprint encodings that work well with users remains massively relevant.

The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as justification for various design choices have been unsubstantiated.

@@

\textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.

@@

\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside any conclusions that can be drawn from the research.

### 2019-08-14 Writeup/Thesis/pages/lit_review.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others. The use-case of E2EE messages will be the primary focus of this paper.

@@

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification. There are, however, issues in how a user should link a key's fingerprint to real world entity. This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.

The fingerprint of the key is generated by running the main key components through a secure one way hash function such as SHA-1. This process produces a digest of fixed length that can be used to compare keys. Therefore, the comparison of expected and actual fingerprints can be used too detect MiTM attacks.
Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
This process is known as the \textit{``authentication ceremony''}. However, system designers are moving away from this structure and are now creating a combined key from each sides' public key. In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of a SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}. This produces a unique key communication pair.
\\\\
Due to the manual comparison of the fingerprint, length and format is a consideration. Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. This rules out the possibility of comparing complete digests. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.

>>>>

Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.

@@

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification. There are, however, issues in how a user should link a key's fingerprint to a real world entity. This paper will, however, assume that users have access to the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.

The fingerprint of the key is generated by running the main key components through a secure one way hash function such as SHA-1. This process produces a digest of fixed length that can be used to compare keys. Therefore, the comparison of expected and actual fingerprints can be used to detect MiTM attacks.
Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
This process is known as the \textit{``authentication ceremony''}. However, system designers are moving away from this structure and are now creating a combined key from each sides' public key. In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of a SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}. This produces a unique key communication pair.
\\\\
Due to the manual comparison of the fingerprint, length and format is a consideration. Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. This rules out the possibility of comparing complete digests. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.

### 2019-08-14 Writeup/Thesis/pages/research_question.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone).}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}. It can be assumed due the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person. This is, therefore, the assumed context the handshake will be occurring in. This means the similarity of words will need to be quantified phonetically instead of visually.

>>>>

By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone).}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}. It can be assumed due to the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person. This is, therefore, the assumed context the handshake will be occurring in. This means the similarity of words will need to be quantified phonetically instead of visually.
